Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-04-10 tese2/13_implementation_model.tex
[ADD] indices until message

\begin{table}[!htb]
\centering
\caption{Schema representation}
\label{table:schema}
    \begin{tabular}{|ll|}
        \hline
        \multicolumn{2}{|c|}{\textbf{Collection name}}       \\ \hline
        $\Diamondblack$ \underline{\_id (primary key)}  & ObjectId   \\ 
        $\medbullet$ Not nullable property name           & Property type                    \\ 
        $\medcirc$ Nullable property name      & Property type                         \\
        $\medcirc$ Reference to document     & ObjectId                         \\
        $\medbullet$ Embedded document      & Document                         \\ 
        $\medbullet$ Embedded list      & List[Type]                         \\ \hline

    \end{tabular}
\end{table}

@@

\begin{table}[!htb]
\centering
\caption{Generic data model}
\label{table:generic}
    \begin{tabular}{cc}
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{Data}}                                \\ \hline
            $\Diamondblack$ \underline{id}  & ObjectId                         \\ 
            $\medbullet$ owner           & ObjectId                            \\ 
            $\medbullet$ properties      & List[Attribute] \\ 
            $\medcirc$ searchableValues & List[Text]        \\ \hline
        \end{tabular}
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{Attribute}}                           \\ \hline
            $\medbullet$ key           & Text                                  \\ 
            $\medcirc$ value           & Object                              \\ 
            $\medbullet$ identifiable    & Boolean                             \\ 
            $\medcirc$ readPermissions &  List[ObjectId]   \\ 
            $\medcirc$ writePermissions  & List[ObjectId]  \\ \hline
        \end{tabular}    
    \end{tabular}
\end{table}

@@

\begin{table}[!htb]
\centering
\caption{User model}
\label{table:user}
    \begin{tabular}{|ll|}
        \hline
        \multicolumn{2}{|c|}{\textbf{User}}                             \\ \hline
        $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
        $\medbullet$ hash           & Text                         \\ 
        $\medbullet$ salt      & Text                         \\ \hline
    \end{tabular}
\end{table}

@@

\begin{table}[!htb]
\centering
\caption{Relation model}
\label{table:relation}
    \begin{tabular}{|ll|}
        \hline
        \multicolumn{2}{|c|}{\textbf{Relation}}                             \\ \hline
        $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
        $\medbullet$ source           & ObjectId                         \\ 
        $\medbullet$ target      & ObjectId                         \\ \hline
    \end{tabular}
\end{table}

@@

@@

\begin{table}[!htb]
\centering
\caption{Group model}
\label{table:group}
    \begin{tabular}{cc}
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{Group}}             \\ \hline
            $\Diamondblack$ \underline{id}  & ObjectId       \\ 
            $\medcirc$ inviteToken           & Text          \\ 
            $\medbullet$ visibility      & Text              \\ \hline
        \end{tabular}

        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{GroupMembership}}   \\ \hline
            $\Diamondblack$ \underline{id}  & ObjectId       \\ 
            $\medbullet$ groupId            & ObjectId        \\ 
            $\medbullet$ userId & ObjectId                   \\ \hline
        \end{tabular}    
    \end{tabular}
\end{table}

@@

@@

\begin{table}[!htb]
\centering
\caption{Message model}
\label{table:message}
    \begin{tabular}{|ll|}
        \hline
        \multicolumn{2}{|c|}{\textbf{Message}}                             \\ \hline
        $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
        $\medbullet$ source           & ObjectId                         \\ 
        $\medbullet$ target      & ObjectId                         \\ 
        $\medbullet$ content      & Text                         \\ \hline
    \end{tabular}
\end{table}

@@

\begin{table}[!htb]
\centering
\caption{Hyper content model}
\label{my-label}
    \begin{tabular}{cc}
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{HyperContent}}                             \\ \hline
            $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
            $\medbullet$ groupId            & ObjectId                         \\ 
            $\medbullet$ start              & Date                         \\ 
            $\medbullet$ end                & Date                         \\ 
            $\medbullet$ content            & Text                         \\ \hline
        \end{tabular}

        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{TimeAnnotation}}                   \\ \hline
            $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
            $\medbullet$ groupId            & ObjectId                         \\ 
            $\medbullet$ title & Text                           \\ 
            $\medbullet$ time & Date                           \\ \hline

@@

\begin{table}[!htb]
\centering
    \caption{Collaborative content model}
    \label{my-label}
    \begin{tabular}{|ll|}
        \hline
        \multicolumn{2}{|c|}{\textbf{CollaborativeContent}}                             \\ \hline
        $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
        $\medbullet$ groupId            & ObjectId                         \\ 
        $\medbullet$ content            & Text                         \\ \hline
    \end{tabular}
\end{table}

@@

\begin{table}[!htb]
\centering
    \caption{Recording model}
    \label{my-label}
    \begin{tabular}{cc}
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{RecordingInterval}}                   \\ \hline
            $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
            $\medbullet$ groupId            & ObjectId                         \\ 
             $\medbullet$ start             & Date                         \\ 
            $\medbullet$ end                & Date                         \\ \hline
        \end{tabular}   
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{RecordingChunk}}                             \\ \hline
            $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
            $\medbullet$ groupId            & ObjectId                         \\ 
            $\medbullet$ owner           & ObjectId                      \\ 
            $\medbullet$ sessionId          & Text                       \\
            $\medbullet$ start              & Date                         \\ 
            $\medbullet$ end                & Date                         \\ 
            $\medbullet$ url               & Text                       \\ \hline
        \end{tabular}
    \end{tabular}
\end{table}

>>>>

\begin{table}[!htb]
\centering
\caption{Schema representation}
\label{table:schema}
    \begin{tabular}{|ll|}
        \hline
        \multicolumn{2}{|c|}{\textbf{Collection name}}              \\ \hline
        $\Diamondblack$ \underline{\_id (primary key)}  & ObjectId  \\ 
        $\medbullet$ Not nullable property name  & Property type    \\ 
        $\medcirc$ Nullable property name      & Property type      \\
        $\medcirc$ Reference to document     & ObjectId             \\
        $\medbullet$ Embedded document      & Document              \\ 
        $\medbullet$ Embedded list      & List[Type]                \\ \hline
    \end{tabular}
\end{table}

@@

\begin{table}[!htb]
\centering
\caption{Generic data model}
\label{table:generic}
    \begin{tabular}{cc}
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{Data}}            \\ \hline
            $\Diamondblack$ \underline{\_id}  & ObjectId     \\ 
            $\medbullet$ owner           & ObjectId        \\ 
            $\medbullet$ properties      & List[Attribute] \\ 
            $\medcirc$ searchableValues & List[Text]       \\ \hline
        \end{tabular}
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{Attribute}}       \\ \hline
            $\medbullet$ key           & Text              \\ 
            $\medcirc$ value           & Object            \\ 
            $\medbullet$ identifiable    & Boolean         \\ 
            $\medcirc$ readPermissions &  List[ObjectId]   \\ 
            $\medcirc$ writePermissions  & List[ObjectId]  \\ \hline
        \end{tabular}    
    \end{tabular}
\end{table}

@@

\begin{table}[!htb]
\centering
\caption{User model}
\label{table:user}
    \begin{tabular}{|ll|}
        \hline
        \multicolumn{2}{|c|}{\textbf{User}}         \\ \hline
        $\Diamondblack$ \underline{\_id}  & ObjectId  \\ 
        $\medbullet$ hash           & Text          \\ 
        $\medbullet$ salt      & Text               \\ \hline
    \end{tabular}
\end{table}

@@

\begin{table}[!htb]
\centering
\caption{Relation model}
\label{table:relation}
    \begin{tabular}{|ll|}
        \hline
        \multicolumn{2}{|c|}{\textbf{Relation}}     \\ \hline
        $\Diamondblack$ \underline{\_id}  & ObjectId  \\ 
        $\medbullet$ source           & ObjectId    \\ 
        $\medbullet$ target      & ObjectId         \\ \hline
    \end{tabular}
\end{table}

@@

In order to improve performance of queries over \emph{Relation} collection we have created indexes on the \emph{source}, \emph{target} and also on the pair composed by both attributes.

@@

\begin{table}[!htb]
\centering
\caption{Group model}
\label{table:group}
    \begin{tabular}{cc}
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{Group}}        \\ \hline
            $\Diamondblack$ \underline{\_id}  & ObjectId  \\ 
            $\medcirc$ inviteToken           & Text     \\ 
            $\medbullet$ visibility      & Text         \\ \hline
        \end{tabular}

        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{GroupMembership}}  \\ \hline
            $\Diamondblack$ \underline{\_id}  & ObjectId      \\ 
            $\medbullet$ groupId            & ObjectId      \\ 
            $\medbullet$ userId & ObjectId                  \\ \hline
        \end{tabular}    
    \end{tabular}
\end{table}

@@

In order to improve performance of queries over \emph{GroupMembership} collection we have created indexes on the \emph{groupId}, \emph{userId} and also on the pair composed by both attributes.

@@

\begin{table}[!htb]
\centering
\caption{Message model}
\label{table:message}
    \begin{tabular}{|ll|}
        \hline
        \multicolumn{2}{|c|}{\textbf{Message}}      \\ \hline
        $\Diamondblack$ \underline{\_id}  & ObjectId  \\ 
        $\medbullet$ source           & ObjectId    \\ 
        $\medbullet$ target      & ObjectId         \\ 
        $\medbullet$ content      & Text            \\ \hline
    \end{tabular}
\end{table}

In order to improve performance of queries over \emph{Relation} collection we have created indexes on the \emph{target} attribute and also on the pair composed by \emph{target} and \emph{\_id} attributes for finding and sorting the messages received by an entity more efficiently.

@@

\begin{table}[!htb]
\centering
\caption{Hyper content model}
\label{my-label}
    \begin{tabular}{cc}
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{HyperContent}}  \\ \hline
            $\Diamondblack$ \underline{\_id}  & ObjectId   \\ 
            $\medbullet$ groupId            & ObjectId   \\ 
            $\medbullet$ start              & Date       \\ 
            $\medbullet$ end                & Date       \\ 
            $\medbullet$ content            & Text       \\ \hline
        \end{tabular}

        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{TimeAnnotation}}  \\ \hline
            $\Diamondblack$ \underline{\_id}  & ObjectId     \\ 
            $\medbullet$ groupId            & ObjectId     \\ 
            $\medbullet$ title & Text                      \\ 
            $\medbullet$ time & Date                       \\ \hline

@@

\begin{table}[!htb]
\centering
    \caption{Collaborative content model}
    \label{my-label}
    \begin{tabular}{|ll|}
        \hline
        \multicolumn{2}{|c|}{\textbf{CollaborativeContent}}  \\ \hline
        $\Diamondblack$ \underline{\_id}  & ObjectId           \\ 
        $\medbullet$ groupId            & ObjectId           \\ 
        $\medbullet$ content            & Text               \\ \hline
    \end{tabular}
\end{table}

@@

\begin{table}[!htb]
\centering
    \caption{Recording model}
    \label{my-label}
    \begin{tabular}{cc}
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{RecordingInterval}}  \\ \hline
            $\Diamondblack$ \underline{\_id}  & ObjectId        \\ 
            $\medbullet$ groupId            & ObjectId        \\ 
             $\medbullet$ start             & Date            \\ 
            $\medbullet$ end                & Date            \\ \hline
        \end{tabular}   
        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{RecordingChunk}}  \\ \hline
            $\Diamondblack$ \underline{\_id}  & ObjectId     \\ 
            $\medbullet$ groupId            & ObjectId     \\ 
            $\medbullet$ owner           & ObjectId        \\ 
            $\medbullet$ sessionId          & Text         \\
            $\medbullet$ start              & Date         \\ 
            $\medbullet$ end                & Date         \\ 
            $\medbullet$ url               & Text          \\ \hline
        \end{tabular}
    \end{tabular}
\end{table}
